|

### 2021-07-20 01-Chp-Background.Rmd
End of day

$$TC \approx LDLc + HDLc + kTG$$
where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).

>>>>

\begin{equation}
  TC \approx LDLc + HDLc + kTG
  (\#eq:total-cholesterol-formula)
\end{equation}

where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).

### 2021-07-20 03-Chp-Systematic-Review.Rmd
End of day

<!-- -   TODO Examine how many times a primary study was included in a review\ -->
<!-- -   TODO Look at whether searching preprints made any difference to my results -->
<!-- -  TODO Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project) -->

@@

@@

$$AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}$$

@@

$$q = \frac{(A+C)+(A+B)}{2N}$$

@@

@@

Need formula here, and description of different methods and quarrels regarding disctinction fixed effect vs random effects meta-analyses.

@@

@@

@@

@@

Table \@ref(tab:incl-studies-character) shows the characteristics [**Include column here that says whether it was included in a systematic review - see below**]

As part of our our forward snowballing exercise (where articles citing an included study are cited), Irecorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis. Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness. This analysis was performed by extracting the citing articles from Google Scholar on [DATE] and screening them manually. The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*

@@

@@

@@

<!----------------------------------------------------------------------------->
### Inclusion of preprints

@@

<!----------------------------------------------------------------------------->
### Open data sharing {#sys-rev-open-data}

@@

<!----------------------------------------------------------------------------->
### Original contribution to research

@@

<!----------------------------------------------------------------------------->
### Comparison with other reviews

@@

<!----------------------------------------------------------------------------->
### Reviewing Mendelian randomisations studies

@@

<!----------------------------------------------------------------------------->
### Strenghts and limitations

@@

>>>>

<!-- -   TODO Examine how many times a primary study was included in a review -->
<!-- -   TODO Look at whether searching preprints made any difference to my results -->
<!-- -  TODO Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project) -->

@@

### Contributions

This systematic review was performed in conjunction with a team of secondary reviewer, all of whom . These included Alexandra MacAleenana, Athena Sheppard, Matthew Lee and Lena Schmidt.

<!-- TODO Double check this list at the end of the project. -->

@@

\begin{equation}
  AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}
  (\#eq:AC1-main)
\end{equation}

@@

\begin{equation}
  q = \frac{(A+C)+(A+B)}{2N}
  (\#eq:AC1-supp)
\end{equation}

@@

In addition, the tool also aim to capture the potential direction of bias for each given domain. An optional question at the end of each domain, e.g. for Domain 1 of the RoB2 tool: "What is the predicted direction of bias arising from the randomization process?", possible responses included

* Not applicable 
* Favours experimental 
* Favours comparator
* Towards null 
* Away from null 
* Unpredictable

@@

Need formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.

@@

\begin{equation}
  weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}
  (\#eq:meta-analysis-fixed)
\end{equation}

where ...

<!-- TODO Need equation for random effects too -->

@@

Following the search

@@

No eligible records were identified in the screening of the 500 records excluded by the search. Many of these were basic science studies <!-- TODO text -->

@@

As part of our our forward snowballing exercise (where articles citing an included study are cited), I recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis. Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness. This analysis was performed by extracting the citing articles from Google Scholar on [DATE] and screening them manually. The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*

@@

Table \@ref(tab:incl-studies-character) shows the characteristics

<!----------------------------------------------------------------------------->
(ref:studyCharacteristics-caption) studyCharacteristics

(ref:studyCharacteristics-scaption) studyCharacteristics

```{r studyCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

@@

### Meta-n

@@

### Inclusion of preprints

@@

### Open data sharing {#sys-rev-open-data}

@@

### Original contribution to research

@@

### Comparison with other reviews

@@

### Reviewing Mendelian randomisations studies

@@

### Strenghts and limitations

@@

## Conclusions

\newpage

### 2021-07-20 04-Chp-CPRD-Analysis.Rmd
End of day

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
options(scipen = 99)
knitr::read_chunk("R/04-Code-CPRD-Analysis.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

$$h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)$$

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
library(dplyr)
options(scipen = 99)
knitr::read_chunk("R/04-Code-CPRD-Analysis.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

\begin{equation}
  h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)
  (\#eq:cox-model)
\end{equation}

### 2021-07-20 front-and-back-matter/99-appendices.Rmd
End of day:
End of day

@@

Impor

@@

wosDatabases_table <- read.csv(here::here("data/sys-rev/wosDatabases.csv"))

if(doc_type == "docx") {
  knitr::kable(wosDatabases_table, caption = "(ref:wosDatabases-caption)")
} else{
  knitr::kable(
    wosDatabases_table,
    format = "latex",
    caption = "(ref:wosDatabases-caption)",
    caption.short = "(ref:wosDatabases-scaption)",
    booktabs = TRUE
  ) %>%
    row_spec(0, bold = TRUE) %>%
    column_spec(column = 1, width = paste0(18,"em")) %>%
    column_spec(column = 2, width = paste0(8,"em")) %>%
    column_spec(column = 3, width = paste0(6,"em")) %>%
    row_spec(2:nrow(wosDatabases_table)-1, hline_after = TRUE) %>%
    kable_styling(latex_options = c("HOLD_position"))
}

@@

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE}
knitr::read_chunk(here::here("R/appendix.R"))
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

<!----------------------------------------------------------------------------->
(ref:searchHits-caption) Overview of the full Medline search strategy.

(ref:searchHits-scaption) searchHits

```{r searchHits-table, message=FALSE, results="asis", echo = FALSE}
```

@@

@@

## Copies of papers arising from this thesis

\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
